Oral contraceptives

### 2021-01-18 r_notebooks/exploring_hydroxychloroquine_sulphate.nb.Rmd
R analyses

```{r setup}
## Packages
devtools::install_github("https://github.com/w-hardy/serCymruTools")
library(tidyverse)
library(lubridate)
library(tsibble)
library(rstan) # needed to load prophet
library(prophet)
library(fable)
library(fable.prophet)
library(feasts)
library(furrr)
library(rebus)
library(MplusAutomation)
library(tidyLPA)
library(serCymruTools)

@@

```{r, health-board-modelling}
plan(multisession)
system.time(hcq_hb_cv_models <-
  regionalCV(data = hcq_monthly_quantity_hb_pre_cv19))
plan(sequential)

hcq_hb_cv_models %>%
  saveRDS("../data/hcq_hb_cv_models.rds")

@@

```{r}
plan(cluster)
system.time(hcq_hb_fcsts <- regionalJointFcsts(hcq_monthly_quantity_hb_pre_cv19))
plan(sequential)

hcq_hb_fcsts %>%
  saveRDS("../data/hcq_hb_fcsts.rds")

@@

```{r, gp-cluster-modelling}
# plan(multisession)
# system.time(hcq_gp_cluster_cv_models <-
#   regionalCV(data = hcq_monthly_quantity_cluster_pre_cv19))
# plan(sequential)
# 
# hcq_gp_cluster_cv_models %>%
#   saveRDS("../data/hcq_gp_cluster_cv_models.rds")

@@

```{r}
# plan(multisession)
# system.time(hcq_gp_cluster_fcsts <- 
#               regionalJointFcsts(hcq_monthly_quantity_cluster_pre_cv19))
# plan(sequential)
# 
# hcq_gp_cluster_fcsts %>%
#   saveRDS("../data/hcq_gp_cluster_fcsts.rds")

@@

```{r, gp-practice-modelling}
incomplete_gp <- hcq_monthly_quantity_gp_pre_cv19 %>% 
    as_tibble() %>% 
    group_by(regional_unit) %>% 
    count() %>% 
    filter(n < 50) %>% 
    .$regional_unit %>% 
    unique()

plan(cluster)
system.time(hcq_gp_cv_models <-
  hcq_monthly_quantity_gp_pre_cv19 %>%
    filter(!regional_unit %in% incomplete_gp) %>%
              regionalCV())
plan(sequential)

hcq_gp_cv_models %>%
  saveRDS("../data/hcq_gp_cv_models.rds")

@@

@@

```{r gp-practice-forecasts}
plan(cluster)
system.time(hcq_gp_fcsts <-
              hcq_monthly_quantity_gp_pre_cv19 %>%
              filter(!regional_unit %in% incomplete_gp) %>%
              regionalJointFcsts())
plan(sequential)

@@

hcq_gp_fcsts %>% 
  group_by(.model) %>% 
  count

@@

@@

```{r}
best_model_gp_discrep %>% 
  filter(discrepancy < -40)

hcq_monthly_quantity_gp %>% 
  filter(regional_unit %in% c("W97009", "W98053")) %>% 
  as_tsibble(key = regional_unit, index = datename) %>% 
  autoplot()

gp %>% 
  filter(practiceid %in% c("W97009", "W98053"))
```

* Based on postcodes, these are both University GPs. Or at least, given their procimity to universities, they will likely have large student populations.

@@

gp_lpa_fit %>%
  plot_profiles(x = ., rawdata = FALSE)

@@

```{r, mplus-anlayses}
source("../r_scripts/functions/mplus_plotting.R")
# mplus_models <- MplusAutomation::readModels("../mplus_analyses/hcq_gp")

@@

# mplus.view.plots("../mplus_analyses/hcq_gp/hcq_discrep_5_class_ml.gh5")
mplus.plot.estimated_means("../mplus_analyses/hcq_gp/hcq_discrep_5_class_ml.gh5")
```
#### kmeans

>>>>

```{r setup}
## Packages
devtools::install_github("https://github.com/w-hardy/serCymruTools")
library(tidyverse)
library(lubridate)
library(tsibble)
library(rstan) # needed to load prophet
library(prophet)
library(fable)
library(fable.prophet)
library(feasts)
library(furrr)
library(rebus)
library(MplusAutomation)
library(tidyLPA)
library(serCymruTools)
library(progressr)
library(beepr)

# handlers(global = TRUE)
# handlers(
#   list(
#     handler_progress(
#       format = ":spin :current/:total (:message) [:bar] :percent in :elapsed ETA: :eta",
#       width = 60,
#       complete = "+"),
#     handler_beepr(finish   = "wilhelm",
#                   interval = 2.0)
#   )
# )

@@

```{r, health-board-modelling}
# plan(multisession)
# with_progress(system.time(hcq_hb_cv_models <-
#   regionalCV(data = hcq_monthly_quantity_hb_pre_cv19)))
# plan(sequential)
# 
# hcq_hb_cv_models %>%
#   saveRDS("../data/hcq_hb_cv_models.rds")

@@

```{r}
# plan(cluster)
# system.time(hcq_hb_fcsts <- regionalJointFcsts(hcq_monthly_quantity_hb_pre_cv19))
# plan(sequential)
# 
# hcq_hb_fcsts %>%
#   saveRDS("../data/hcq_hb_fcsts.rds")

@@

```{r, gp-cluster-modelling}
plan(multisession)
system.time(hcq_gp_cluster_cv_models <-
  regionalCV(data = hcq_monthly_quantity_cluster_pre_cv19))
plan(sequential)

hcq_gp_cluster_cv_models %>%
  saveRDS("../data/hcq_gp_cluster_cv_models.rds")

@@

```{r}
plan(multisession)
system.time(hcq_gp_cluster_fcsts <-
              regionalJointFcsts(hcq_monthly_quantity_cluster_pre_cv19))
plan(sequential)

hcq_gp_cluster_fcsts %>%
  saveRDS("../data/hcq_gp_cluster_fcsts.rds")

@@

```{r, gp-practice-modelling}
complete_gp <- 
  hcq_monthly_quantity_gp_pre_cv19 %>% 
  as_tibble() %>% 
  group_by(regional_unit) %>% 
  count() %>% 
  filter(n >= 62) %>% 
  .$regional_unit %>% 
  unique()

# plan(multisession)
# # Chunking analyses into ~100 GPs uses ~ 23Gb of RAM
# system.time(hcq_gp_cv_models_1 <-
#   hcq_monthly_quantity_gp_pre_cv19 %>%
#     filter(regional_unit %in% complete_gp[1:100]) %>% 
#               regionalCV(init = 48))
# system.time(hcq_gp_cv_models_2 <-
#   hcq_monthly_quantity_gp_pre_cv19 %>%
#     filter(regional_unit %in% complete_gp[101:200]) %>% 
#               regionalCV(init = 48))
# system.time(hcq_gp_cv_models_3 <-
#   hcq_monthly_quantity_gp_pre_cv19 %>%
#     filter(regional_unit %in% complete_gp[201:300]) %>% 
#               regionalCV(init = 48))
# system.time(hcq_gp_cv_models_4 <-
#   hcq_monthly_quantity_gp_pre_cv19 %>%
#     filter(regional_unit %in% complete_gp[301:length(complete_gp)]) %>% 
#               regionalCV(init = 48))
# plan(sequential)
# 
# hcq_gp_cv_models <- 
#   bind_rows(hcq_gp_cv_models_1,
#             hcq_gp_cv_models_2,
#             hcq_gp_cv_models_3,
#             hcq_gp_cv_models_4)
# 
# hcq_gp_cv_models %>%
#   saveRDS("../data/hcq_gp_cv_models.rds")

@@

hcq_monthly_quantity_gp_pre_cv19 %>% 
  as_tibble() %>% 
  group_by(regional_unit) %>% 
  summarise(mean_quantity = mean(n))

best_model_gp %>% 
  left_join(hcq_monthly_quantity_gp_pre_cv19 %>% 
              as_tibble() %>% 
              group_by(regional_unit) %>% 
              summarise(mean_quantity = mean(n)), 
            by = c("regional_unit")) %>% 
  select(-c(.model, .type)) %>% 
  DataExplorer::plot_correlation()

@@

```{r gp-practice-forecasts}
plan(cluster)
system.time(hcq_gp_fcsts <-
              hcq_monthly_quantity_gp_pre_cv19 %>%
              filter(regional_unit %in% complete_gp) %>%
              regionalJointFcsts())
plan(sequential)

@@

@@

* 2755.011 seconds 2021-01-13

@@

@@

gp_lpa_fit %>%
  plot_profiles(x = ., rawdata = FALSE)
```

@@

```{r, mplus-anlayses, eval=FALSE}
source("../r_scripts/functions/mplus_plotting.R")
# mplus_models <- MplusAutomation::readModels("../mplus_analyses/hcq_gp")

@@

# mplus.view.plots("../mplus_analyses/hcq_gp/hcq_discrep_3_class_lgmm_ml.gh5")
mplus.plot.estimated_means("../mplus_analyses/hcq_gp/hcq_discrep_3_class_lgmm_ml.gh5")
```

#### kmeans

### 2021-01-18 r_notebooks/exploring_oral_anticoagulants_war_prop.Rmd
R analyses

propRegional <- function(data, region, datename = datename, unit = Quantity, 
                         bnf){
  # Function to create tsibble object for a proportion of a drug by a given `unit` 
  # per `datename`
  # e.g. propRegional(oc, Locality, datename, Quantity) is the `Quantity`
  # per `datename` grouped by `Locality` from `oc`. `Quantity` is corrected for
  # the number of days in each month.
  region <- enquo(region)
  datename <- enquo(datename)
  unit <- enquo(unit)

  data %>%
    mutate(regional_unit = as_factor(set_names(!!region))) %>%
    group_by(!!datename, bnfchem, regional_unit) %>% 
    summarise(n = sum(!!unit)) %>% 
    mutate(n = 100 * n / sum(n),
           log_n = log(n)) %>% 
    filter(bnfchem == bnf) %>%
    ungroup() %>%
    as_tsibble(index = !!datename, key = regional_unit)
}

@@

  # joint_fit <-
  #   left_join(fable_fit, prophet_fit, by = "regional_unit")
  joint_fcst <-
    bind_rows(fable_fcst, prophet_fcst) %>%
    mutate(lb_95 = quantile(n, .025),
           lb_80 = quantile(n, .1),
           med = median(n),
           ub_80 = quantile(n, .9),
           ub_95 = quantile(n, .975),
           sd = distributional::variance(n)^2,
           dist = n,
           n = NULL)

@@

# oac_p_monthly_quantity_hb_pre_cv19 <- 
#   oac_p_monthly_quantity_hb %>% 
#     filter(datename < dmy("01-03-2020"))
# 
# oac_p_monthly_quantity_cluster_pre_cv19 <- 
#   oac_p_monthly_quantity_cluster %>% 
#     filter(datename < dmy("01-03-2020"))

@@

* 965.17 seconds with prophetModelsBound() 2021-01-15

@@

oac_p_hb_fcsts <- 
  read_rds("../data/oac_p_hb_fcsts.rds")
```
129.80 2021-01-15
*

@@

# Running regionalCV() on each of the quarter of the data
plan(multisession)
system.time(oac_p_gp_cv_models_1 <-
  complete_oac_p_monthly_quantity_gp_pre_cv19_1 %>%
              regionalCV())
system.time(oac_p_gp_cv_models_2 <-
  complete_oac_p_monthly_quantity_gp_pre_cv19_2 %>%
              regionalCV())
system.time(oac_p_gp_cv_models_3 <-
  complete_oac_p_monthly_quantity_gp_pre_cv19_3 %>%
              regionalCV())
system.time(oac_p_gp_cv_models_4 <-
  complete_oac_p_monthly_quantity_gp_pre_cv19_4 %>%
              regionalCV())
plan(sequential)

>>>>

propRegional <- function(data, region, datename = datename, unit = Quantity, 
                         bnf){
  # Function to create tsibble object for a proportion of a drug by a given `unit` 
  # per `datename`
  # e.g. propRegional(oc, Locality, datename, Quantity) is the `Quantity`
  # per `datename` grouped by `Locality` from `oc`

  region <- enquo(region)
  datename <- enquo(datename)
  unit <- enquo(unit)

  data %>%
    mutate(regional_unit = as_factor(set_names(!!region))) %>%
    group_by(regional_unit, !!datename, bnfchem) %>% 
    summarise(n = sum(!!unit), .groups = "drop_last") %>% 
    mutate(n = 100 * n / sum(n)) %>% 
    filter(bnfchem == bnf) %>%
    ungroup() %>%
    as_tsibble(index = !!datename, key = regional_unit)
}

@@

  # joint_fit <-
  #   left_join(fable_fit, prophet_fit, by = "regional_unit")
  joint_fcst <-
    bind_rows(fable_fcst, prophet_fcst) %>%
    mutate(lb_95 = quantile(n, .025),
           lb_80 = quantile(n, .1),
           med = median(n),
           ub_80 = quantile(n, .9),
           ub_95 = quantile(n, .975),
           sd = distributional::variance(n)^2,
           n = NULL # Remove distribution from saved object
           )

@@

oac_p_monthly_quantity_hb_pre_cv19 <-
  oac_p_monthly_quantity_hb %>%
    filter(datename < dmy("01-03-2020"))

oac_p_monthly_quantity_cluster_pre_cv19 <-
  oac_p_monthly_quantity_cluster %>%
    filter(datename < dmy("01-03-2020"))

@@

* 965.17 seconds with prophetModelsBound() 2021-01-15
* 966.923 seconds with prophetModelsBound() 2021-01-18

@@

oac_p_hb_fcsts <- 
  read_rds("../data/oac_p_hb_fcsts.rds")
```

* 129.80 2021-01-15
* 107.254 2021-01-18

@@

# Running regionalCV() on each of the quarter of the data
plan(cluster)
system.time(oac_p_gp_cv_models_1 <-
  complete_oac_p_monthly_quantity_gp_pre_cv19_1 %>%
              regionalCV())
system.time(oac_p_gp_cv_models_2 <-
  complete_oac_p_monthly_quantity_gp_pre_cv19_2 %>%
              regionalCV())
plan(sequential)
system.time(oac_p_gp_cv_models_3 <-
  complete_oac_p_monthly_quantity_gp_pre_cv19_3 %>%
              regionalCV())
system.time(oac_p_gp_cv_models_4 <-
  complete_oac_p_monthly_quantity_gp_pre_cv19_4 %>%
              regionalCV())
plan(sequential)

### 2021-01-18 r_notebooks/exploring_oral_contraceptives.Rmd
R analyses

```{r, health-board-modelling}
# plan(multisession)
# system.time(oc_hb_cv_models <-
#   regionalCV(data = oc_monthly_quantity_hb_pre_cv19))
# plan(sequential)
# 
# oc_hb_cv_models %>%
#   saveRDS("../data/oc_hb_cv_models.rds")

oc_hb_cv_models <- 
  read_rds("../data/oc_hb_cv_models.rds")

@@

* 570.350 seconds with multisession prophetModels()

@@

```{r, gp-cluster-modelling}
# plan(multisession)
# system.time(oc_gp_cluster_cv_models <-
#   regionalCV(data = oc_monthly_quantity_cluster_pre_cv19))
# plan(sequential)
# 
# oc_gp_cluster_cv_models %>%
#   saveRDS("../data/oc_gp_cluster_cv_models.rds")

@@

oc_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  ggplot(aes(x = MAPE)) +
  geom_histogram()

>>>>

```{r, health-board-modelling}
plan(multisession)
system.time(oc_hb_cv_models <-
  regionalCV(data = oc_monthly_quantity_hb_pre_cv19))
plan(sequential)

# oc_hb_cv_models %>%
#   saveRDS("../data/oc_hb_cv_models.rds")
# 
# oc_hb_cv_models <- 
#   read_rds("../data/oc_hb_cv_models.rds")

@@

* 570.350 seconds with multisession prophetModels()
* 278.968 seconds 2021-01-18

@@

```{r, gp-cluster-modelling}
plan(multisession)
system.time(oc_gp_cluster_cv_models <-
  regionalCV(data = oc_monthly_quantity_cluster_pre_cv19))
plan(sequential)
# 
# oc_gp_cluster_cv_models %>%
#   saveRDS("../data/oc_gp_cluster_cv_models.rds")

@@

oc_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  ggplot(aes(x = MAPE)) +
  geom_histogram() +
  coord_cartesian(ylim = c(0,100))
